The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-10-07 manuscript/manuscript.tex
Update while writing the "reply to the referee"

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling are also provided by this work through a common procedure for spectral model fits. This approach first correct the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. {\bf The stellar mass of these 27 object have been estimated using multi-band imaging data, and we adopt them to compare the \mbh-\smass\ relation.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

{\bf The value for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2). The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}

@@

{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm. Then, we subtract the globe sky background light to obtain the clear image. To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative. Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}

@@

We simultaneously fit the two-dimensional flux distribution of the central AGN and the underlying host galaxy. Following common practice, we model the central AGN as a scaled point source and the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be more complicated (e.g., bulge+disk). However, the \sersic\ model is an adequate first-order approximation of the surface brightness distribution with a flexible parameterization that provides sufficient freedom to infer the total host flux even for our high redshift sample. We simultaneously fit the nearby galaxies, that happen to be close enough to the AGN, with a \sersic\ model to account for any potential contamination from their extended profiles. The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model; thus, we mask these objects in the fitting procedure.

@@

In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates. Thus, the choice of template is a subdominant source of error. {\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since we only select the AGN sample that have {\it measured} \mbh\ falls into our selection window. The detailed analysis on this effect is beyond the scope. In our forthcoming paper, we focus on the sample scatter.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.

@@

To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}. In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor. We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution. {\bf In this paper, we aim to make the differential measurement as function of redshift. With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure. This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s. galaxy stellar masses, bulge v.s. total and \mbh\ by single epoch v.s. reverberation v.s. dynamical.

@@

For the local by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)). This is beyond the comparison medium, i.e., bulge v.s. disk, of ours. Moreover, with a more manageable model, our inference gets ride of the overfitting issue. In spite of this, when adopting the \citet{Bentz2018} as local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
 }

@@

\begin{table}
\centering
\caption{The summary for the comparison sample}\label{tab:comp_sample}
\resizebox{18cm}{!}{
\begin{minipage}{0.5\textwidth}
\begin{tabular}{l c  p{2cm}c   c  }
\hline\hline
Object ID$^a$ & $z$ & $\log$\smass\ & $\log$\mbh \\
&&$(M_{\odot}$)&$(M_{\odot}$)\\ \\
\hline\hline
\multicolumn{2}{l}{Local sample by \citet{H+R04}}\\
\hline 
M87 & 0.0037$^b$ & 11.78$^c$$\pm$0.18 & 9.48$\pm$0.2 \\
NGC1068 & 0.0035 & 10.36$\pm$0.18 & 7.15$\pm$0.1 \\
NGC3379 & 0.0025 & 10.83$\pm$0.18 & 8.00$\pm$0.1 \\
NGC4374 & 0.0043 & 11.56$\pm$0.18 & 8.63$\pm$0.2 \\
NGC4261 & 0.0073 & 11.56$\pm$0.18 & 8.72$\pm$0.3 \\
NGC6251 & 0.0243 & 11.75$\pm$0.18 & 8.72$\pm$0.3 \\
NGC7052 & 0.0136 & 11.46$\pm$0.18 & 8.52$\pm$0.2 \\
NGC4742 & 0.0036 & 9.79$\pm$0.18 & 7.15$\pm$0.2 \\
NGC821 & 0.0056 & 11.11$\pm$0.18 & 7.57$\pm$0.2 \\
IC1459 & 0.0068 & 11.46$\pm$0.18 & 9.40$\pm$0.4 \\
M31 & 0.0002 & 10.57$\pm$0.18 & 7.65$\pm$0.2 \\
M32 & 0.0002 & 8.90$\pm$0.18 & 6.40$\pm$0.3 \\
NGC1023 & 0.0027 & 10.84$\pm$0.18 & 7.64$\pm$0.5 \\
NGC2778 & 0.0053 & 10.88$\pm$0.18 & 7.15$\pm$0.2 \\
NGC3115 & 0.0023 & 11.08$\pm$0.18 & 9.00$\pm$0.2 \\
NGC3245 & 0.0049 & 10.83$\pm$0.18 & 8.32$\pm$0.3 \\
NGC3377 & 0.0026 & 10.20$\pm$0.18 & 8.00$\pm$0.6 \\
NGC3384 & 0.0027 & 10.30$\pm$0.18 & 7.20$\pm$0.4 \\
NGC3608 & 0.0053 & 10.99$\pm$0.18 & 8.28$\pm$0.3 \\
NGC4291 & 0.0061 & 11.11$\pm$0.18 & 8.49$\pm$0.2 \\
NGC4342 & 0.0036 & 10.08$\pm$0.18 & 8.48$\pm$0.2 \\
NGC4473 & 0.0037 & 10.96$\pm$0.18 & 8.04$\pm$0.6 \\
NGC4564 & 0.0035 & 10.64$\pm$0.18 & 7.75$\pm$0.4 \\
NGC4594 & 0.0023 & 11.43$\pm$0.18 & 9.00$\pm$0.3 \\
NGC4649 & 0.0039 & 11.69$\pm$0.18 & 9.30$\pm$0.0 \\
NGC4697 & 0.0027 & 11.04$\pm$0.18 & 8.23$\pm$0.6 \\
NGC5845 & 0.0060 & 10.57$\pm$0.18 & 8.38$\pm$0.1 \\
NGC7332 & 0.0053 & 10.18$\pm$0.18 & 7.11$\pm$0.2 \\
NGC7457 & 0.0031 & 9.85$\pm$0.18 & 6.54$\pm$0.1 \\
Milky Way & 0.0000 & 10.04$\pm$0.18 & 6.57$\pm$0.2 \\
\hline\hline
\multicolumn{2}{l}{Local sample by \citet{Bennert++2011}}\\
\hline
0121$-$0102 & 0.0540 & 10.12$\pm$0.24 & 7.44$\pm$0.4 \\
0206$-$0017 & 0.0430 & 10.95$\pm$0.23 & 8.01$\pm$0.4 \\
0353$-$0623 & 0.0760 & 10.33$\pm$0.22 & 7.44$\pm$0.4 \\
0802$+$3104 & 0.0410 & 10.38$\pm$0.23 & 7.17$\pm$0.4 \\
0846$+$2522 & 0.0510 & 10.50$\pm$0.23 & 8.52$\pm$0.4 \\
1042$+$0414 & 0.0524 & 10.32$\pm$0.23 & 6.98$\pm$0.4 \\
1043$+$1105 & 0.0475 & 9.83$\pm$0.24 & 7.67$\pm$0.4 \\
1049$+$2451 & 0.0550 & 10.41$\pm$0.23 & 7.84$\pm$0.4 \\
1101$+$1102 & 0.0355 & 10.33$\pm$0.22 & 7.77$\pm$0.4 \\
1116$+$4123 & 0.0210 & 10.20$\pm$0.22 & 7.37$\pm$0.4 \\
1144$+$3653 & 0.0380 & 10.26$\pm$0.22 & 7.36$\pm$0.4 \\
1210$+$3820 & 0.0229 & 9.94$\pm$0.24 & 7.50$\pm$0.4 \\
1250$-$0249 & 0.0470 & 10.14$\pm$0.22 & 7.65$\pm$0.4 \\
1323$+$2701 & 0.0559 & 9.65$\pm$0.22 & 6.98$\pm$0.4 \\
1355$+$3834 & 0.0501 & 10.11$\pm$0.23 & 7.96$\pm$0.4 \\
1405$-$0259 & 0.0541 & 10.04$\pm$0.23 & 7.08$\pm$0.4 \\
1419$+$0754 & 0.0558 & 10.73$\pm$0.21 & 7.51$\pm$0.4 \\
1434$+$4839 & 0.0365 & 10.30$\pm$0.24 & 7.48$\pm$0.4 \\
1535$+$5754 & 0.0304 & 10.24$\pm$0.24 & 7.83$\pm$0.4 \\
1545$+$1709 & 0.0481 & 9.92$\pm$0.22 & 7.28$\pm$0.4 \\
1554$+$3238 & 0.0483 & 10.00$\pm$0.23 & 7.63$\pm$0.4 \\
1557$+$0830 & 0.0465 & 9.82$\pm$0.23 & 7.55$\pm$0.4 \\
1605$+$3305 & 0.0532 & 9.95$\pm$0.23 & 7.78$\pm$0.4 \\
1606$+$3324 & 0.0585 & 10.33$\pm$0.22 & 7.22$\pm$0.4 \\
1611$+$5211 & 0.0409 & 10.33$\pm$0.22 & 7.34$\pm$0.4 \\
\hline\hline
 \\\\ \\\\ \\

>>>>

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits. This approach first correct the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data. For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples. The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex. {\bf Note that the B10 only provide the galaxy single V-band luminosity. In \citet{Ding2017b}, the galaxy R-band luminosity are derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04). It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample. In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the sample stellar template. Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

{\bf The values for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2). The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}

@@

{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution. Then, we subtract the globe sky background light to obtain the clear image. To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative. Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}

@@

We simultaneously fit the two-dimensional flux distribution of the central AGN and the underlying host galaxy. Following common practice, we model the central AGN as a scaled point source and the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be more complicated (e.g., bulge$+$disk). However, the \sersic\ model is an adequate first-order approximation of the surface brightness distribution with a flexible parameterization that provides sufficient freedom to infer the total host flux even for our high redshift sample. We simultaneously fit the nearby galaxies, that happen to be close enough to the AGN, with a \sersic\ model to account for any potential contamination from their extended profiles. The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model; thus, we mask these objects in the fitting procedure.

@@

In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates. Thus, the choice of template is a subdominant source of error. {\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since only the AGN sample that has {\it measured} \mbh\ falls into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) would be selected.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.

@@

To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}. In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor. We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution. {\bf We also note the limitations of the local sample we current adopted. For instance, the morphological features like strong bars in B10 were not considered in the decomposition, which might affect the inference of the bulge/disk properties. Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling. These issues have been addressed in the discussions in~\citet{Kormendy13} in detail. Even so, we adopt the B10 and HR04 as our comparison local sample given the following reasons. In this study, we aim to make the differential measurement as function of redshift. With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure. This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s. galaxy stellar masses, bulge v.s. total and \mbh\ by single epoch v.s. reverberation v.s. dynamical.

@@

For the local sample by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)). This is beyond the comparison medium, i.e., bulge v.s. disk, of ours. Moreover, with a more manageable model, our inference gets ride of the overfitting issue. In spite of this, when adopting the \citet{Bentz2018} as local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
 }

@@

\begin{table}
\centering
\caption{The summary for the comparison \mbh-\smass\ sample}\label{tab:comp_sample}
\resizebox{18cm}{!}{
\begin{minipage}{0.5\textwidth}
\begin{tabular}{l c  p{2cm}c   c  }
\hline\hline
Object ID$^a$ & $z$ & $\log$\smass\ & $\log$\mbh \\
&&$(M_{\odot}$)&$(M_{\odot}$)\\ \\
\hline\hline
\multicolumn{2}{l}{Local sample by \citet{H+R04}}\\
\hline 
M87 & 0.0037$^b$ & 11.78$^c$$\pm$0.18 & 9.48$\pm$0.2 \\
NGC1068 & 0.0035 & 10.36$\pm$0.18 & 7.15$\pm$0.1 \\
NGC3379 & 0.0025 & 10.83$\pm$0.18 & 8.00$\pm$0.1 \\
NGC4374 & 0.0043 & 11.56$\pm$0.18 & 8.63$\pm$0.2 \\
NGC4261 & 0.0073 & 11.56$\pm$0.18 & 8.72$\pm$0.3 \\
NGC6251 & 0.0243 & 11.75$\pm$0.18 & 8.72$\pm$0.3 \\
NGC7052 & 0.0136 & 11.46$\pm$0.18 & 8.52$\pm$0.2 \\
NGC4742 & 0.0036 & 9.79$\pm$0.18 & 7.15$\pm$0.2 \\
NGC821 & 0.0056 & 11.11$\pm$0.18 & 7.57$\pm$0.2 \\
IC1459 & 0.0068 & 11.46$\pm$0.18 & 9.40$\pm$0.4 \\
M31 & 0.0002 & 10.57$\pm$0.18 & 7.65$\pm$0.2 \\
M32 & 0.0002 & 8.90$\pm$0.18 & 6.40$\pm$0.3 \\
NGC1023 & 0.0027 & 10.84$\pm$0.18 & 7.64$\pm$0.5 \\
NGC2778 & 0.0053 & 10.88$\pm$0.18 & 7.15$\pm$0.2 \\
NGC3115 & 0.0023 & 11.08$\pm$0.18 & 9.00$\pm$0.2 \\
NGC3245 & 0.0049 & 10.83$\pm$0.18 & 8.32$\pm$0.3 \\
NGC3377 & 0.0026 & 10.20$\pm$0.18 & 8.00$\pm$0.6 \\
NGC3384 & 0.0027 & 10.30$\pm$0.18 & 7.20$\pm$0.4 \\
NGC3608 & 0.0053 & 10.99$\pm$0.18 & 8.28$\pm$0.3 \\
NGC4291 & 0.0061 & 11.11$\pm$0.18 & 8.49$\pm$0.2 \\
NGC4342 & 0.0036 & 10.08$\pm$0.18 & 8.48$\pm$0.2 \\
NGC4473 & 0.0037 & 10.96$\pm$0.18 & 8.04$\pm$0.6 \\
NGC4564 & 0.0035 & 10.64$\pm$0.18 & 7.75$\pm$0.4 \\
NGC4594 & 0.0023 & 11.43$\pm$0.18 & 9.00$\pm$0.3 \\
NGC4649 & 0.0039 & 11.69$\pm$0.18 & 9.30$\pm$0.0 \\
NGC4697 & 0.0027 & 11.04$\pm$0.18 & 8.23$\pm$0.6 \\
NGC5845 & 0.0060 & 10.57$\pm$0.18 & 8.38$\pm$0.1 \\
NGC7332 & 0.0053 & 10.18$\pm$0.18 & 7.11$\pm$0.2 \\
NGC7457 & 0.0031 & 9.85$\pm$0.18 & 6.54$\pm$0.1 \\
Milky Way & 0.0000 & 10.04$\pm$0.18 & 6.57$\pm$0.2 \\
\hline\hline
\multicolumn{2}{l}{Local sample by \citet{Bennert++2011}}\\
\hline
0121$-$0102 & 0.0540 & 10.12$\pm$0.24 & 7.44$\pm$0.4 \\
0206$-$0017 & 0.0430 & 10.95$\pm$0.23 & 8.01$\pm$0.4 \\
0353$-$0623 & 0.0760 & 10.33$\pm$0.22 & 7.44$\pm$0.4 \\
0802$+$3104 & 0.0410 & 10.38$\pm$0.23 & 7.17$\pm$0.4 \\
0846$+$2522 & 0.0510 & 10.50$\pm$0.23 & 8.52$\pm$0.4 \\
1042$+$0414 & 0.0524 & 10.32$\pm$0.23 & 6.98$\pm$0.4 \\
1043$+$1105 & 0.0475 & 9.83$\pm$0.24 & 7.67$\pm$0.4 \\
1049$+$2451 & 0.0550 & 10.41$\pm$0.23 & 7.84$\pm$0.4 \\
1101$+$1102 & 0.0355 & 10.33$\pm$0.22 & 7.77$\pm$0.4 \\
1116$+$4123 & 0.0210 & 10.20$\pm$0.22 & 7.37$\pm$0.4 \\
1144$+$3653 & 0.0380 & 10.26$\pm$0.22 & 7.36$\pm$0.4 \\
1210$+$3820 & 0.0229 & 9.94$\pm$0.24 & 7.50$\pm$0.4 \\
1250$-$0249 & 0.0470 & 10.14$\pm$0.22 & 7.65$\pm$0.4 \\
1323$+$2701 & 0.0559 & 9.65$\pm$0.22 & 6.98$\pm$0.4 \\
1355$+$3834 & 0.0501 & 10.11$\pm$0.23 & 7.96$\pm$0.4 \\
1405$-$0259 & 0.0541 & 10.04$\pm$0.23 & 7.08$\pm$0.4 \\
1419$+$0754 & 0.0558 & 10.73$\pm$0.21 & 7.51$\pm$0.4 \\
1434$+$4839 & 0.0365 & 10.30$\pm$0.24 & 7.48$\pm$0.4 \\
1535$+$5754 & 0.0304 & 10.24$\pm$0.24 & 7.83$\pm$0.4 \\
1545$+$1709 & 0.0481 & 9.92$\pm$0.22 & 7.28$\pm$0.4 \\
1554$+$3238 & 0.0483 & 10.00$\pm$0.23 & 7.63$\pm$0.4 \\
1557$+$0830 & 0.0465 & 9.82$\pm$0.23 & 7.55$\pm$0.4 \\
1605$+$3305 & 0.0532 & 9.95$\pm$0.23 & 7.78$\pm$0.4 \\
1606$+$3324 & 0.0585 & 10.33$\pm$0.22 & 7.22$\pm$0.4 \\
1611$+$5211 & 0.0409 & 10.33$\pm$0.22 & 7.34$\pm$0.4 \\
\hline\hline
 \\\\ \\\\ \\
